Draft for project

### 2014-11-17 draft_project.tex
BLÆHBLÆBLÆBLÆBLÆBLÆBLÆBLÆgit add .git add .

	\item[Control of the temporal derivative:] The derivation of (\ref{temporal_bound}) holds up in this case and we have
	\begin{equation*}
	\iint_{Q_T} \Phi'_n(u_n)|\partial_t u_n|^2 dxdt \leq \iint_{Q_T} \left\{ -\partial_t f_n \Phi_n(u_n) + Cf_n\partial_tf_n \right\} dxdt.
	\end{equation*}
	Just to reiterate, $C$ is here the constant given by Poincaré inequality, and is as such only dependent on $\Omega$.

@@

See now that
\begin{align*}
\nabla z_n &= Z_n'(u_n)\nabla u_n \\
	&\leq \Phi_n'(u_n)\nabla u_n \\
	&= \nabla \Phi_n(u_n) \\
	&= \nabla w_n,
\end{align*}
which means that $|\nabla z_n|^2 \leq |\nabla w_n|^2$ in all of $Q_T$.
\end{proof}

>>>>

	\item[Control of the temporal derivative:] The derivation of (\ref{temporal_bound}) holds up in this case and we have
	\begin{equation*}
	\label{exist_proof_temporal}
	\iint_{Q_T} \Phi'_n(u_n)|\partial_t u_n|^2 dxdt \leq \iint_{Q_T} \left\{ -\partial_t f_n \Phi_n(u_n) + Cf_n\partial_tf_n \right\} dxdt.
	\end{equation*}
	Just to reiterate, $C$ is here the constant given by Poincaré inequality, and is as such only dependent on $\Omega$.

@@

See now that
\begin{align*}
\nabla z_n &= Z_n'(u_n)\nabla u_n \\
	&\leq \Phi_n'(u_n)\nabla u_n \\
	&= \nabla \Phi_n(u_n) \\
	&= \nabla w_n,
\end{align*}
which means that $|\nabla z_n|^2 \leq |\nabla w_n|^2$ in all of $Q_T$. As a trivial consequence of this
\begin{equation*}
\iint_{Q_T}|\nabla z_n|^2dxdt \leq \iint_{Q_T}|\nabla w_n|^2dxdt.
\end{equation*}

Seeing as estimate (\ref{exist_proof_spatial}), we can argue exactly as we did in the previous proof to say that $\nabla z_n$ is uniformly bounded in $L^2(Q_T)$.
Similarly we have the two inequalities
\begin{equation*}
|\partial_t z_n | \leq |\partial_t u_n|, \quad \text{ and} \quad |\partial_t z_n| \leq |\Phi_n'(u_n) \partial_t u_n|,
\end{equation*}
and as a consequence
\begin{equation*}
\iint_{Q_T}|\partial_t z_n|^2 dxdt \leq \iint_{Q_T} |\Phi_n'(u_n)|\cdot |\partial_t u_n|^2dxdt.
\end{equation*}
The estimate (\ref{exist_proof_temporal}) holds in this case as well, and by the assumptions on $f$ and its approximations we also have a uniform bound of $\partial_t z_n$ in $L^2(Q_T)$. Hence $z_n$ is a bounded sequence in $H^1(Q_T)$, and we can utilize the Rellich-Kondrachov Compactness Theorem (theorem \ref{Rellich}) again to conclude that there is a subsequence $\{z_{n_j}\}$ converging to some $z$ in $L^2(Q_T)$.
\end{proof}
